Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-05-21 tex/test-WW-type-00v-PS.tex
tex

\newcommand{\SB}[1]{{\bf SB:} {\color{magenta} #1}}
\newcommand{\judge}[1]{{\boldmath \ ({\lowercase\blue{#1}}, PS)}}

@@

%\date{\today}
%===================  PREPRINT NUMBER, JOURNAL =======================
%\
%===================  ABSTRACT =======================================
%\begin{abstract}
\abstract{ 
We present the complete cross-section for pion production in semi-inclusive 
deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in 
the Wandzura--Wilczek-type approximation \ps{which consists in a systematic
neglect of $q\bar q g$-terms with respect to $\bar{q}q$-correlators.}
We compute all twist-2 and twist-3 structure functions and the corresponding 
asymmetries, and discuss the applicability of the Wandzura--Wilczek-type 
approximations on the basis of available data. We make predictions which 
can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future 
Electron-Ion Collider. The results of this paper can be readily used for 
phenomenology and for event generators, and will help to improve our 
understanding of the TMD theory beyond leading twist.
} 
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons, 
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura--Wilczek approximation, 
	semi-inclusive deep inelastic scattering, 
	transverse momentum dependent distribution functions, 
	spin and azimuthal asymmetries, leading and subleading twist}

@@

A great deal of what is known about the quark-gluon structure of 
nucleon is due to studies of parton distribution functions (PDFs) 
in deep-inelastic reactions. leading--twist PDFs  tell us  how likely 
it is to find an unpolarized parton 
(described by PDF $f_1^a(x)$, $a=q,\,\bar q,\,g$) 
or a longitudinally polarized parton 
(described by PDF $g_1^a(x)$, $a=q,\,\bar q,\,g$)
in a fast-moving unpolarized or longitudinally polarized nucleon, 
which carries the fraction $x$ of the nucleon momentum.
This information depends on the ``resolution (renormalization) scale'' 
associated with the hard scale $Q$ of the process.
%, which we will not indicate for notational simplicity.
Although the PDFs  $f_1^a(x)$ and $g_1^a(x)$ continue being the 
subject of intense research (small-$x$, large-$x$, helicity sea 
and gluon distributions) they can be considered as rather 
well-known, and the frontier has been extended in the last years 
to go beyond the one-dimensional picture offered by those PDFs.

@@

In QCD the TMDs are independent functions. Each TMD contains unique
information on a different aspect of the nucleon structure. 
Twist-2 TMDs have partonic interpretations. Twist-3 TMDs 
give insights on quark-gluon correlations in the nucleon
\cite{Miller:2007ae,Burkardt:2007rv,Burkardt:2009rf}. 
Besides positivity constraints \cite{Bacchetta:1999kz} 
there is little model-independent information on TMDs. 
An important question with practical applications is:
do useful {\sl approximations} for TMDs exist? 
Experience from collinear PDFs encourages to explore this possibility: 
the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be expressed in terms of 
contributions from twist-2 $g_1^a(x)$ and $h_1^a(x)$, and additional 
quark-gluon-quark ($\bar{q}gq$) correlations or current quark mass 
terms \cite{Wandzura:1977qf,Jaffe:1991ra}. 
We shall refer to the latter generically as $\bar qgq$-terms, keeping in 
mind one deals in each case with matrix elements of different operators.
The $\bar qgq$-correlations contain new insights on hadron structure 
which are worthwhile exploring for their own sake, 
see \cite{Jaffe:1989xx} on $g_T^a(x)$.

The striking observation is that the $\bar qgq$-terms in $g_T^a(x)$ 
and $h_L^a(x)$ are small: theoretical mechanisms predict this 
\cite{Balla:1997hf,Dressler:1999hc,Gockeler:2000ja,Gockeler:2005vw}, 
and in the case of $g_T^a(x)$ data confirm or are compatible with these 
predictions \cite{Abe:1998wq,Anthony:2002hy,Airapetian:2011wu}.
This approximation (``neglect of $\bar qgq$-terms'') is commonly 
known as Wandzura--Wilczek (WW) approximation \cite{Wandzura:1977qf}.
The possibility to apply this type of approximation also to TMDs has 
been explored in specific cases in \cite{Kotzinian:1995cz,Kotzinian:1997wt,
Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk,Tangerman:1994bb}.
In both cases, PDFs and TMDs, one basically assumes that the 
contributions from $\bar{q}gq$-terms can be neglected with respect to 
$\bar{q}q$-terms. But the nature of the omitted matrix elements is 
different, and in the context of TMDs one often prefers to speak 
about WW-type approximations.

@@

This is the first study of all SIDIS structure functions up to twist-3 
in a unique approach. Our results are of importance for experiments prepared 
in the near-term (JLab 12, \ps{COMPASS}) or proposed in the long-term 
(Electron Ion Collider), and provide helpful input for Monte Carlo event
generators \cite{Avakian:2015vha}.
Our predictions will either be confirmed within the expected accuracy
\ps{or not be supported by data. The first case will call for dedicated 
theoretical studies to explain why the pertinent $\bar{q}gq$-terms are 
so small. The second case will call for explanations why sometimes 
$\bar{q}gq$-terms are so sizable. In this way our work will help to guide 
further developments. In either case our results will deepen the
understanding of the quark-gluon correlations inside hadrons.}

@@

The SIDIS process is sketched in 
Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
lepton and nucleon, and $l^\prime$ and $P_h$ are the momenta of the outgoing
electron and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
selects a z-axis, and $l^\prime$ points in the direction of the x-axis 
from which azimuthal angles are counted. The relevant kinematic invariants 
are
\ba
   x  = \frac{Q^2}{2\,P\cdot  q}, \;\;
   y = \frac{P \cdot  q}{P \cdot  l}, \;\;
   z = \frac{P \cdot  P_h}{P\cdot  q}, \;\;
%   \gamma = \frac{2 M x}{Q} \; .
   Q^2=-q^2.
\label{eq:xyz}\;\;\;\;\ea
In addition to $x$, $y$, $z$ the cross section is also differential 
in the azimuthal angle $\phi_h$ of the produced hadron, the square 
of its momentum component $\Phperp$ perpendicular with respect to the 
virtual photon momentum. 
\ps{In principle the cross section is also differential with respect to the} 
azimuthal angle $\psi_l$ characterizing the overall orientation of the 
lepton scattering plane in \ps{a fixed} lab frame.
%
% Notice that $d \psi_l \simeq d\phi_S$ where $\phi_S$ is the azimuthal angle
% of the nucleon spin vector. 
%
\ps{By analyzing the data in the reference frame in Fig.~\ref{fig-kin-SIDIS}
all events are by definition in the ``bin'' $\psi_l=0$ (within detector
resolution) and the variable $\psi_l$ is practically integrated out leaving 
us with a 5-dimensional cross section. Below we keep the cross section 
``differential'' in $\psi_l$ for symbolic reasons.}
%
It is convenient to define the unpolarized
lepton--quark scattering \ps{subprocess} cross section
\ba\label{Eq:sigma0-FUU}
	% \sigma_0 \equiv 
	\frac{d \hat{\sigma}}{dy} 
	= 
	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
	\biggl(1-y+\frac12y^2\biggr)\;
\ea

@@

At subleading order \ps{in the $1/Q$ expansion} one has
\ba\hspace{-1cm}
   &&   \frac{d^6\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
   =	\frac{1}{4\pi} \; \frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z,\Phperp^2)
        \Biggl\{ 
          \cos(\phi_h)\,p_3\,A_{UU}^{\cos(\phi_h)}
	\nonumber\\ 
   && \hspace{2cm}
	+ \lambda\sin(\phi_h)\,p_4\,A_{LU}^{\sin(\phi_h)}+ S_L\sin(\phi_h)\,p_3\,A_{UL}^{\sin(\phi_h)}    
	+ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} \phantom{\frac11}\nonumber\\ 
   && \hspace{2cm}
	+ S_T\sin(2\phi_h-\phi_S)\,p_3\,A_{UT}^{\sin(2\phi_h-\phi_S)}
        + \lambda\,S_L\cos(\phi_h)\,p_4\,A_{LL}^{\cos(\phi_h)}\phantom{\frac11}
	\nonumber\\
   && \hspace{2cm}
  	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
        + \lambda\,S_T\cos(2\phi_h-\phi_S)\,p_4\,A_{LT}^{\cos(2\phi_h-\phi_S)}
	\Biggr\}
   \hspace{1cm} \label{Eq:SIDIS-subleading}
\ea\end{subequations}
Neglecting $1/Q^2$ corrections, the kinematic prefactors $p_i$ are given by 
% \ba\label{Eq:y-prefactors}
% &&	p_1 = \varepsilon \equiv  
%        \frac{1-y -\frac{1}{4}\slim \gamma^2 y^2}{1-y
%        + \frac{1}{2}\slim y^2 +\frac{1}{4}\slim \gamma^2 y^2} 
%        \approx \frac{1-y}{1-y+\frac12\,y^2} 		\;,\nonumber\\
% &&	p_2 = \sqrt{1-\epsilon^2} \approx
%        \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2} 	\;,\nonumber\\
% &&	p_3 =  \sqrt{2\varepsilon(1+\varepsilon)}
%        \approx \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2}\;,\nonumber\\
% &&	p_4 =  \sqrt{2\varepsilon(1-\varepsilon)}
%        \approx \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2} 	\;,\;\;\;
% \ea
\be\label{Eq:y-prefactors}
	p_1 = \frac{1-y}{1-y+\frac12\,y^2} 		\, , \;\;\;
	p_2 = \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2}	\, , \;\;\;
	p_3 = \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2} 	\, , \;\;\;
	p_4 = \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2}     	\, .
\ee
and the asymmetries are defined as 
\be
	A_{XY}^{\rm weight}\equiv A_{XY}^{\rm weight}(x,z,\Phperp)=
	\frac{F_{XY}^{\rm weight}(x,z,\Phperp)}{F_{UU}(x,z,\Phperp)}.
\ee
Hereby the first index $X=U(L)$ denotes the unpolarized beam
(longitudinally polarized beam with helicity $\lambda$).
The second index $Y=U(L,T)$ refers to the target which can be unpolarized
(or longitudinally, transversely polarized with respect to virtual photon).
The superscript ``weight'' indicates the azimuthal dependence with no index 
indicating an isotropic angular distribution of the produced hadrons.

@@

Experimental collaborations often define asymmetries in terms of counts 
$N(\phi_h)$. This means the kinematic prefactors $p_i$ and $1/(x\,y\,Q^2)$ 
are included in the numerators or denominators of the asymmetries which
are averaged over $y$ within experimental kinematics. We will call the 
corresponding asymmetries $\asympre{XY}{\rm weight}$.
For instance, in unpolarized case one has 
\be
	N(x,\dots,\phi) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
		+ \cos\phi\;\asympre{UU}{\cos\phi_h}(x,\dots)
		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
\ee
where $N_0$ denotes the total ($\phi_h$-averaged) number of counts 
and the dots indicate further kinematic variables in the kinematic 
bin of interest (which may also be averaged over).
It would be preferable if asymmetries were analyzed with known kinematic 
prefactors divided out on event-by-event basis. One could then directly 
compare asymmetries $\asym{XY}{\rm weight}$ measured in different 
experiments and kinematics, and focus on effects of evolution 
or power suppression for twist-3. In practice, often the kinematic 
factors were included. We will define and comment on the explicit 
expressions as needed.

@@

TMDs are defined in terms of light-front correlators
\be\label{Eq:correlator}
    	\Phi(x,\bfkperp)_{ij} = \int\frac{ d \xi^- d^2{\bm \xi}_\perp}{(2\pi)^3}
	\;e^{ik\xi}\;\la N(P,S)|\bar\psi_j(0)\,{\cal W}_{(0,\,\infty)}
	{\cal W}_{(\infty,\xi)}\,\psi_i(\xi)|N(P,S)\ra
    	\with{ }{\xi^+\!=\!0}{$k^+ = xP^+$}
	\ee
where the % symbolic 
Wilson-lines refer to the SIDIS process 
\cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
the light-cone coordinates $a^\mu=(a^+,a^-,a_\perp)$ with 
$a^\pm=(a^0\pm a^3)/\sqrt{2}$. 
The light-cone direction is singled out by the virtual photon momentum 
and transverse vectors like $\bfkperp$ are perpendicular to it. In the
virtual-photon--nucleon center-of-mass frame, nucleon and the partons 
inside it move in the $(+)$-lightcone direction, while the struck 
quark and the produced hadron move in $(-)$-light-cone direction.
In the nucleon rest frame the polarization vector is given by 
$S=(0,{\bm S}_T,S_L)$ with ${\bm S}_T^2+S_L^2=1$.

@@

Other structures drop out either due to explicit $\kperp$-dependence,

@@

The structures surviving $\Phperp$-integration of the SIDIS cross section in 
(\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
are associated with the trivial weights $\omega^{\{0\}}$ and expressed in 
terms of collinear PDFs and FFs as follows (here the 
sum rules (\ref{Eq:sum-rules-T-odd}) are used)
\begin{subequations}\ba
	F_{UU}(x,z) &=& x\sum\limits_ae_a^2\,f_1^a(x)\,D_1^a(z)
	\label{Eq:FUU-collinear}\\
	F_{LL}(x,z) &=& x\sum\limits_ae_a^2\,g_1^a(x)\,D_1^a(z)
	\label{Eq:FLL-collinear}\\
 	F_{LT}^{\cos\phi_S}(x,z) &=& -\,\frac{2M_N}{Q}\; x\sum_a e_a^2\,
	\biggl(x\,g_T^q(x) + r_h\,h_1^a(x)\frac{\tilde{E}^a(z)}{z}\biggr)
	\label{Eq:FLT-collinear}\\
	 F_{UT}^{\sin\phi_S}(x,z) &=& -\,\frac{2\,m_h}{Q}\; x\sum_a e_a^2\,
	h_1^a(x)\frac{\tilde{H}^a(z)}{z}
	\label{Eq:FUT-collinear}
\ea\end{subequations}
Finally, \ps{integrating over $z$, summing over hadrons, and} 
using the sum rules for the T-odd FFs 
$\sum_h\int d z\;\tilde{E}^a(z)=0$ and
$\sum_h\int d z\;\tilde{H}^a(z)=0$ we recover
Eqs.~(\ref{Eq:DIS-F1}--\ref{Eq:DIS-zero}) and obtain for the DIS structure 
functions
\begin{subequations}\ba
    F_1(x) & = & \frac{1}{2}\sum_a e_a^2\,f_1^a(x) \label{Eq:DIS-F1-II}\\
    g_1(x) & = & \frac{1}{2}\sum_a e_a^2\,g_1^a(x) \label{Eq:DIS-g1-II}\\
    g_2(x) & = & \frac{1}{2}\sum_a e_a^2\,g_T^a(x)\;-\;g_1(x) \label{Eq:DIS-g2}
	\hspace{25mm}
\ea\end{subequations}
Having established the notation we now define and discuss the
approximations.

@@

In this section we will define the approximations and review what is
known about them.
The basic idea of the approximations is simple. One \ps{uses QCD
equations of motion to separate contributions from $\bar{q}q$-terms 
and $\bar{q}gq$-terms and assumes that the latter} can be neglected 
with respect to \ps{the leading} $\bar{q}q$-terms with a useful accuracy,
\be\label{Eq:WW-generic}
	\biggl|\frac{\la\bar{q}gq\ra}{\la\bar{q}q\ra}\biggr| \ll 1\,.
\ee

@@

The origin of the approximations is as follows.
The operators defining $g_T^a(x)$ and~$h_L^a(x)$ can be decomposed by means 
of QCD equations of motion in twist-2 parts, and pure twist-3 
(interaction dependent) $\bar qgq$-terms and current quark mass
terms. We denote $\bar qgq$-terms and mass-terms collectively 
and symbolically by functions with a tilde.
Such decompositions are possible because $g_T^a(x)$ and $h_L^a(x)$ are 
``twist-3'' not according to the ``strict QCD definition''
(twist $=$ mass dimension of associated local operator minus its spin).
Rather they are classified according to the ``working definition'' 
\cite{Jaffe:1996zw}  
(a function is ``twist $t$'' if it contributes to cross sections
suppressed by $(M/Q)^{t-2}$ with $M$ a generic hadronic and $Q$ the 
hard scale).
The two definitions coincide for twist-2 quantities, but higher twist
observables in general contain ``contaminations'' by leading twist.

>>>>

\newcommand{\SB}[1]{{\bf SB:} {\color{magenta} #1}}

@@

%\date{\today}
%===================  PREPRINT NUMBER, JOURNAL =======================
%\
%===================  ABSTRACT =======================================
%\begin{abstract}
\abstract{ 
We present the complete cross-section for pion production in semi-inclusive 
deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in 
the Wandzura--Wilczek-type approximation \ps{which consists in a systematic
neglect of $\bar{q}gq$--terms with respect to $\bar{q}q$--correlators.}
We compute all twist-2 and twist-3 structure functions and the corresponding 
asymmetries, and discuss the applicability of the Wandzura--Wilczek-type 
approximations on the basis of available data. We make predictions which 
can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future 
Electron-Ion Collider. The results of this paper can be readily used for 
phenomenology and for event generators, and will help to improve our 
understanding of the TMD theory beyond leading twist.
} 
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons, 
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura--Wilczek approximation, 
	semi-inclusive deep inelastic scattering, 
	transverse momentum dependent distribution functions, 
	spin and azimuthal asymmetries, leading and subleading twist}

@@

A great deal of what is known about the quark-gluon structure of 
nucleon is due to studies of parton distribution functions (PDFs) 
in deep-inelastic reactions. leading--twist PDFs  tell us  how likely 
it is to find an unpolarized parton 
(described by PDF $f_1^a(x)$, $a=q,\,\bar q,\,g$) 
or a longitudinally polarized parton 
(described by PDF $g_1^a(x)$, $a=q,\,\bar q,\,g$)
in a fast-moving unpolarized or longitudinally polarized nucleon, 
which carries the fraction $x$ of the nucleon momentum.
This information depends on the ``resolution (renormalization) scale'' 
associated with the hard scale $Q$ of the process.
Although the PDFs  $f_1^a(x)$ and $g_1^a(x)$ continue being the 
subject of intense research (small-$x$, large-$x$, helicity sea 
and gluon distributions) they can be considered as rather 
well-known, and the frontier has been extended in the last years 
to go beyond the one-dimensional picture offered by those PDFs.

@@

In QCD the TMDs are independent functions. Each TMD contains unique
information on a different aspect of the nucleon structure. 
Twist-2 TMDs have partonic interpretations. Twist-3 TMDs 
give insights on quark-gluon correlations in the nucleon
\cite{Miller:2007ae,Burkardt:2007rv,Burkardt:2009rf}. 
Besides positivity constraints \cite{Bacchetta:1999kz} 
there is little model-independent information on TMDs. 
An important question with practical applications is:
do useful {\sl approximations} for TMDs exist? 
Experience from collinear PDFs encourages to explore this possibility: 
the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be expressed in terms of 
contributions from twist-2 $g_1^a(x)$ and $h_1^a(x)$, and additional 
quark-gluon-quark ($\bar{q}gq$) correlations or current quark mass 
terms \cite{Wandzura:1977qf,Jaffe:1991ra}. 
We shall refer to the latter generically as $\bar qgq$--terms, keeping in 
mind one deals in each case with matrix elements of different operators.
The $\bar qgq$--correlations contain new insights on hadron structure 
which are worthwhile exploring for their own sake, 
see \cite{Jaffe:1989xx} on $g_T^a(x)$.

The striking observation is that the $\bar qgq$--terms in $g_T^a(x)$ 
and $h_L^a(x)$ are small: theoretical mechanisms predict this 
\cite{Balla:1997hf,Dressler:1999hc,Gockeler:2000ja,Gockeler:2005vw}, 
and in the case of $g_T^a(x)$ data confirm or are compatible with these 
predictions \cite{Abe:1998wq,Anthony:2002hy,Airapetian:2011wu}.
This approximation (``neglect of $\bar qgq$--terms'') is commonly 
known as Wandzura--Wilczek (WW) approximation \cite{Wandzura:1977qf}.
The possibility to apply this type of approximation also to TMDs has 
been explored in specific cases in \cite{Kotzinian:1995cz,Kotzinian:1997wt,
Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk,Tangerman:1994bb}.
In both cases, PDFs and TMDs, one basically assumes that the 
contributions from $\bar{q}gq$--terms can be neglected with respect to 
$\bar{q}q$--terms. But the nature of the omitted matrix elements is 
different, and in the context of TMDs one often prefers to speak 
about WW-type approximations.

@@

This is the first study of all SIDIS structure functions up to twist-3 
in a unique approach. Our results are of importance for experiments prepared 
in the near-term at \ps{Jefferson Lab (JLab) with 12$\,$GeV beam energy
upgrade and COMPASS} or proposed in the long-term  
(Electron Ion Collider), and provide helpful input for Monte Carlo event
generators \cite{Avakian:2015vha}.

Our predictions will either be confirmed within the expected accuracy
\ps{or not supported by data. This will call for dedicated theoretical 
studies to explain either why the pertinent $\bar{q}gq$--terms are 
so small or so sizable. In either case our results will deepen the 
understanding of  $\bar{q}gq$--correlations and help to guide 
further developments.}

@@

The SIDIS process is sketched in 
Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
lepton and nucleon, and $l^\prime$ and $P_h$ are the momenta of the outgoing
electron and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
selects a z-axis, and $l^\prime$ points in the direction of the x-axis 
from which azimuthal angles are counted. The relevant kinematic invariants 
are
\ba
   x  = \frac{Q^2}{2\,P\cdot  q}, \;\;
   y = \frac{P \cdot  q}{P \cdot  l}, \;\;
   z = \frac{P \cdot  P_h}{P\cdot  q}, \;\;
%   \gamma = \frac{2 M x}{Q} \; .
   Q^2=-q^2.
\label{eq:xyz}\;\;\;\;\ea
In addition to $x$, $y$, $z$ the cross section is also differential 
in the azimuthal angle $\phi_h$ of the produced hadron, the square 
of its momentum component $\Phperp$ perpendicular with respect to the 
virtual photon momentum. 
In principle the cross section is also differential with respect to the
azimuthal angle $\psi_l$ characterizing the overall orientation of the 
lepton scattering plane in a fixed lab frame.
\ps{By analyzing the data in the reference frame in Fig.~\ref{fig-kin-SIDIS}
all events are by definition in the ``bin'' $\psi_l=0$ (within detector
resolution) and the variable $\psi_l$ is practically integrated out leaving 
us with a 5-dimensional cross section. Below we keep the cross section 
``differential'' in $\psi_l$ for symbolic reasons.} 
It is convenient to define the unpolarized 
lepton--quark scattering subprocess cross section
\ba\label{Eq:sigma0-FUU}
	% \sigma_0 \equiv 
	\frac{d \hat{\sigma}}{dy} 
	= 
	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
	\biggl(1-y+\frac12y^2\biggr)\;
\ea

@@

At subleading order in the $1/Q$ expansion one has
\ba\hspace{-1cm}
   &&   \frac{d^6\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
   =	\frac{1}{4\pi} \; \frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z,\Phperp^2)
        \Biggl\{ 
          \cos(\phi_h)\,p_3\,A_{UU}^{\cos(\phi_h)}
	\nonumber\\ 
   && \hspace{2cm}
	+ \lambda\sin(\phi_h)\,p_4\,A_{LU}^{\sin(\phi_h)}+ S_L\sin(\phi_h)\,p_3\,A_{UL}^{\sin(\phi_h)}    
	+ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} \phantom{\frac11}\nonumber\\ 
   && \hspace{2cm}
	+ S_T\sin(2\phi_h-\phi_S)\,p_3\,A_{UT}^{\sin(2\phi_h-\phi_S)}
        + \lambda\,S_L\cos(\phi_h)\,p_4\,A_{LL}^{\cos(\phi_h)}\phantom{\frac11}
	\nonumber\\
   && \hspace{2cm}
  	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
        + \lambda\,S_T\cos(2\phi_h-\phi_S)\,p_4\,A_{LT}^{\cos(2\phi_h-\phi_S)}
	\Biggr\}
   \hspace{1cm} \label{Eq:SIDIS-subleading}
\ea\end{subequations}
Neglecting $1/Q^2$ corrections, the kinematic prefactors $p_i$ are given by 
% \ba\label{Eq:y-prefactors}
% &&	p_1 = \varepsilon \equiv  
%        \frac{1-y -\frac{1}{4}\slim \gamma^2 y^2}{1-y
%        + \frac{1}{2}\slim y^2 +\frac{1}{4}\slim \gamma^2 y^2} 
%        \approx \frac{1-y}{1-y+\frac12\,y^2} 		\;,\nonumber\\
% &&	p_2 = \sqrt{1-\epsilon^2} \approx
%        \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2} 	\;,\nonumber\\
% &&	p_3 =  \sqrt{2\varepsilon(1+\varepsilon)}
%        \approx \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2}\;,\nonumber\\
% &&	p_4 =  \sqrt{2\varepsilon(1-\varepsilon)}
%        \approx \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2} 	\;,\;\;\;
% \ea
\be\label{Eq:y-prefactors}
	p_1 = \frac{1-y}{1-y+\frac12\,y^2} 		\, , \;\;\;
	p_2 = \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2}	\, , \;\;\;
	p_3 = \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2} 	\, , \;\;\;
	p_4 = \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2}     	\, .
\ee
and the asymmetries are defined as 
\be
	A_{XY}^{\rm weight}\equiv A_{XY}^{\rm weight}(x,z,\Phperp)=
	\frac{F_{XY}^{\rm weight}(x,z,\Phperp)}{F_{UU}(x,z,\Phperp)}.
\ee
Hereby the first index $X=U(L)$ denotes the unpolarized beam
(longitudinally polarized beam with helicity $\lambda$).
The second index $Y=U(L,T)$ refers to the target which can be unpolarized
(or longitudinally, transversely polarized with respect to virtual photon).
The superscript ``weight'' indicates the azimuthal dependence with no index 
indicating an isotropic angular distribution of the produced hadrons.

@@

Experimental collaborations often define asymmetries in terms of counts 
$N(\phi_h)$. This means the kinematic prefactors $p_i$ and $1/(x\,y\,Q^2)$ 
are included in the numerators or denominators of the asymmetries which
are averaged over $y$ within experimental kinematics. We will call the 
corresponding asymmetries $\asympre{XY}{\rm weight}$.
For instance, in unpolarized case one has 
\be
	N(x,\dots,\phi) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
		+ \cos\phi\;\asympre{UU}{\cos\phi_h}(x,\dots)
		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
\ee
where $N_0$ denotes the total ($\phi_h$--averaged) number of counts 
and the dots indicate further kinematic variables in the kinematic 
bin of interest (which may also be averaged over).
It would be preferable if asymmetries were analyzed with known kinematic 
prefactors divided out on event-by-event basis. One could then directly 
compare asymmetries $\asym{XY}{\rm weight}$ measured in different 
experiments and kinematics, and focus on effects of evolution 
or power suppression for twist-3. In practice, often the kinematic 
factors were included. We will define and comment on the explicit 
expressions as needed.

@@

TMDs are defined in terms of light-front correlators
\be\label{Eq:correlator}
    	\Phi(x,\bfkperp)_{ij} = \int\frac{ d \xi^- d^2{\bm \xi}_\perp}{(2\pi)^3}
	\;e^{ik\xi}\;\la N(P,S)|\bar\psi_j(0)\,{\cal W}_{(0,\,\infty)}
	{\cal W}_{(\infty,\xi)}\,\psi_i(\xi)|N(P,S)\ra
    	\with{ }{\xi^+\!=\!0}{$k^+ = xP^+$}
	\ee
where the % symbolic 
Wilson-lines refer to the SIDIS process 
\cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
the light-cone coordinates $a^\mu=(a^+,a^-,a_\perp)$ with 
$a^\pm=(a^0\pm a^3)/\sqrt{2}$. 
The light-cone direction is singled out by the virtual photon momentum 
and transverse vectors like $\bfkperp$ are perpendicular to it. In the
virtual-photon--nucleon center-of-mass frame, nucleon and the partons 
inside it move in the $(+)$--lightcone direction, while the struck 
quark and the produced hadron move in $(-)$--light-cone direction.
In the nucleon rest frame the polarization vector is given by 
$S=(0,{\bm S}_T,S_L)$ with ${\bm S}_T^2+S_L^2=1$.

@@

Other structures drop out either due to explicit $\kperp$--dependence,

@@

The structures surviving $\Phperp$--integration of the SIDIS cross section in 
(\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
are associated with the trivial weights $\omega^{\{0\}}$ and expressed in 
terms of collinear PDFs and FFs as follows (here the 
sum rules (\ref{Eq:sum-rules-T-odd}) are used)
\begin{subequations}\ba
	F_{UU}(x,z) &=& x\sum\limits_ae_a^2\,f_1^a(x)\,D_1^a(z)
	\label{Eq:FUU-collinear}\\
	F_{LL}(x,z) &=& x\sum\limits_ae_a^2\,g_1^a(x)\,D_1^a(z)
	\label{Eq:FLL-collinear}\\
 	F_{LT}^{\cos\phi_S}(x,z) &=& -\,\frac{2M_N}{Q}\; x\sum_a e_a^2\,
	\biggl(x\,g_T^q(x)\,D_1^a(z)+r_h\,h_1^a(x)\frac{\tilde{E}^a(z)}{z}\biggr)
	\label{Eq:FLT-collinear}\\
	 F_{UT}^{\sin\phi_S}(x,z) &=& -\,\frac{2\,m_h}{Q}\; x\sum_a e_a^2\,
	h_1^a(x)\frac{\tilde{H}^a(z)}{z}
	\label{Eq:FUT-collinear}
\ea\end{subequations}
Finally, integrating over $z$, summing over hadrons, and 
using the sum rules for the T-odd FFs 
$\sum_h\int d z\;\tilde{E}^a(z)=0$ and
$\sum_h\int d z\;\tilde{H}^a(z)=0$ we recover
Eqs.~(\ref{Eq:DIS-F1}--\ref{Eq:DIS-zero}) and obtain for the DIS structure 
functions
\begin{subequations}\ba
    F_1(x) & = & \frac{1}{2}\sum_a e_a^2\,f_1^a(x) \label{Eq:DIS-F1-II}\\
    g_1(x) & = & \frac{1}{2}\sum_a e_a^2\,g_1^a(x) \label{Eq:DIS-g1-II}\\
    g_2(x) & = & \frac{1}{2}\sum_a e_a^2\,g_T^a(x)\;-\;g_1(x) \label{Eq:DIS-g2}
	\hspace{25mm}
\ea\end{subequations}
Having established the notation we now define and discuss the
approximations.

@@

In this section we will define the approximations and review what is
known about them.
The basic idea of the approximations is simple. One uses QCD
equations of motion to separate contributions from $\bar{q}q$--terms 
and $\bar{q}gq$--terms and assumes that the latter can be neglected 
with respect to the leading $\bar{q}q$--terms with a useful accuracy,
\be\label{Eq:WW-generic}
	\biggl|\frac{\la\bar{q}gq\ra}{\la\bar{q}q\ra}\biggr| \ll 1\,.
\ee

@@

The origin of the approximations is as follows.
The operators defining $g_T^a(x)$ and~$h_L^a(x)$ can be decomposed by means 
of QCD equations of motion in twist-2 parts, and pure twist-3 
(interaction dependent) $\bar qgq$--terms and current quark mass
terms. We denote $\bar qgq$--terms and mass-terms collectively 
and symbolically by functions with a tilde.
Such decompositions are possible because $g_T^a(x)$ and $h_L^a(x)$ are 
``twist-3'' not according to the ``strict QCD definition''
(twist $=$ mass dimension of associated local operator minus its spin).
Rather they are classified according to the ``working definition'' 
\cite{Jaffe:1996zw}  
(a function is ``twist $t$'' if it contributes to cross sections
suppressed by $(M/Q)^{t-2}$ with $M$ a generic hadronic and $Q$ the 
hard scale).
The two definitions coincide for twist-2 quantities, but higher twist
observables in general contain ``contaminations'' by leading twist.
